\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[grey]{classic}
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Vitaly}
\familyname{Bragilevsky}
\title{Curriculum Vitae}
\address{Zorge St. 15, 63}{344090, Rostov-on-Don, Russia}
\mobile{+7 (960) 461-51-06}
\phone{+7 (863) 300-76-63}
\email{vit.bragilevsky@gmail.com}
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{1997--2001}{B.Sc. in Applied Mathematics and Computer Science}{Rostov State University}{Rostov-on-Don, Russia}
{\textit{with honours}}{}
\cventry{2001--2003}{M.Sc. in Applied Mathematics and Computer Science}{Rostov State University}{Rostov-on-Don, Russia}
{\textit{with honours}}{Major in mathematical physics.}
\cventry{2004, December}{Short course in methods, tools and systems for information security}
{Moscow Engineering Physics Institute}{Moscow, Russia}{}{}
\cventry{2010, November--December}{Short course in hardware and software for computer networking}
{Southern Federal University}{Rostov-on-Don, Russia}{}{}
\cventry{2011,\\June 16--July 1}{10th Annual Oregon Programming Languages Summer School
(Types, Semantics and Verification)}
{University of Oregon}{Eugene, OR, USA}{}{}
\cventry{2011,\\August 2--14}{Summer School Marktoberdorf 2011 
(Tools for Analysis and Verification of Software Safety and Security)}
{Technische Universität München}{Bayrischzell}{}{}


\section{Master thesis}
\cvline{title}{\emph{Singular-type operators in the spaces of vector-valued functions.}}
\cvline{supervisor}{Prof. V.S. Pilidi}
\cvline{description}{\small Algebras of operators of singular and bisingular type are considered. For these algebras, 
the notions of an envelope of a family of operators are introduced, 
necessary and sufficient conditions of its existence and uniqueness are given. 
There are obtained estimates for the essential norm of the envelope operator. 
The statements of the paper are demonstrated for the case of singular integral 
operators with continuous operator-valued coefficients.}

\section{Experience}
%\subsection{Vocational}
\cventry{2003--present}{Lecturer/Teaching assistant}{Southern Federal University (former Rostov State University), Department of Mathematics, Mechanics and Computer Science}{Rostov-on-Don}{Russia}
{Courses: Web/XML-technologies (2003–2008), Computer networks (2005, 2006), Distributed systems (2007, 2008), 
 Operating systems (2008–2010),  Programming in Java (2008–2010), 
Functional programming (2009, 2011), 
Abstract algebra and number theory for Cryptography (2010, 2011), 
Computer methods in discrete mathematics (2010, 2011).\\
Practice/labs: Programming languages (2003–2009), Logic and computability (2011).}

% \subsection{Miscellaneous}
% \cventry{2002--present}{Teacher}{Children's Computer School (at the Southern Federal University)}{Rostov-on-Don}{Russia}
% {Teaching: beginner's courses in computing and programming (Pascal).}

% \renewcommand{\listitemsymbol}{-} % change the symbol for lists


% \section{Education: Courses}
% \subsection{University Examinations (all with excellent marks)}
% \cvlistdoubleitem{Calculus I, II}{Geometry}
% \cvlistdoubleitem{Linear Algebra}{Differential Equations}
% \cvlistdoubleitem{Computer Science}{Programming Languages}
% \cvlistdoubleitem{Physics}{Optimization Methods}
% \cvlistdoubleitem{Functional Analysis}{Theoretical Mechanics}
% \cvlistdoubleitem{Discrete Mathematics}{Advanced Topics in Mechanics}
% \cvlistdoubleitem{Partial Differential Equations in Mathematical Physics}{Mathematical Models in Natural Sciences}
% \cvlistdoubleitem{Numeric Computations}{Asymptotic Methods}
% \cvlistdoubleitem{Analysis of Algorithms}{Graph Algorithms}
% \cvlistdoubleitem{Digital Signal Processing}{Continuum Mechanics}
% \cvlistdoubleitem{Algebraic coding theory}{Modern Numeric Computations}
% \cvlistdoubleitem{Advanced Calculus}{Advanced Algebra}
% \cvlistdoubleitem{Algebra for information security}{Theory of Probability and Mathematical Statistics}
% \cvlistdoubleitem{Parallel computations}{}
% \subsection{Other University Courses}
% \cvlistdoubleitem{Operations Research}{The Theory of Random Processes}
% \cvlistdoubleitem{Supercomputers}{Computer Networks}
% \cvlistdoubleitem{Databases}{Object-oriented Programming (C++)}
% \cvlistdoubleitem{Delphi Programming Language}{Windows API Programming}


% \subsection{Self-study}
% \cvlistitem{Structure and Interpretation of Computer Programs (using book by Hal Abelson, Jerry Sussman and Julie Sussman)}
% \cvlistitem{Category Theory for Computing Science (using book by M. Barr and C. Wells)}
% \cvlistitem{Foundations of Programming Languages (using book by J. Mitchell)}
% \cvlistitem{Type Theory (using book by B. Pierce)}

\section{Publications (in Russian)}
\cvlistitem{V. Bragilevsky, V. S. Pilidi. Analog of Simonenko's theorem on an envelope of a family of operators for operators on the spaces of vector-valued functions.
Izvestia vuzov. Severokavkazsky region. Vol. 4. 2005.}
\cvlistitem{V. Bragilevsky. Limits of Folds Expressiveness. Practice of Functional Programming. Vol.~4. 2010.}

\section{Interests}
\cvline{History}{\small Medieval Europe}
\cvline{Arts}{\small 19th century music and literature}
\cvline{Project Euler}{\small Solving interesting algorithmic problems}
\cvline{}{\small (personal profile: \url{http://projecteuler.net/profile/bravit.png})}

\end{document}
